\documentclass{article}
\usepackage{longtable}
\usepackage[pdfauthor={flonatel},%
pdftitle={Requirment for rmtoo},%
pdfsubject={Requirment description for rmtoo},%
pdfkeywords={requirments management tool open source dependency tracking},%
pagebackref=true,%
pdftex, bookmarks=true, colorlinks=true]{hyperref}

\usepackage[a4paper]{geometry}

\parindent0em

\begin{document}
\thispagestyle{empty}

\mbox{}

\vfill

{\LARGE\textbf{Requirements for rmtoo}}

\vfill

{\Large\textbf{written by Andreas Florath}}

\vfill

07. March 2010

\vfill

\newpage

\mbox{}

\vfill

{\small

\copyright 2010 by florath nanosystems \& telecommunications GmbH \& Co. KG
--- www.flonatel.org 

All rights reserved.

Redistribution and use in physical and binary forms, with or without
modification, are permitted provided that the following conditions are
met:

Redistributions must retain the above copyright notice, this list of
conditions and the following disclaimer.

Neither the name of the florath nanosystems \& telecommunications GmbH
\& Co. KG nor the names of its contributors may be used to endorse or
promote products derived from this software without specific prior
written permission.

THIS DOCUMENTATION IS PROVIDED BY THE COPYRIGHT HOLDERS AND
CONTRIBUTORS "AS IS" AND ANY EXPRESS OR IMPLIED WARRANTIES, INCLUDING,
BUT NOT LIMITED TO, THE IMPLIED WARRANTIES OF MERCHANTABILITY AND
FITNESS FOR A PARTICULAR PURPOSE ARE DISCLAIMED. IN NO EVENT SHALL THE
COPYRIGHT OWNER OR CONTRIBUTORS BE LIABLE FOR ANY DIRECT, INDIRECT,
INCIDENTAL, SPECIAL, EXEMPLARY, OR CONSEQUENTIAL DAMAGES (INCLUDING,
BUT NOT LIMITED TO, PROCUREMENT OF SUBSTITUTE GOODS OR SERVICES; LOSS
OF USE, DATA, OR PROFITS; OR BUSINESS INTERRUPTION) HOWEVER CAUSED AND
ON ANY THEORY OF LIABILITY, WHETHER IN CONTRACT, STRICT LIABILITY, OR
TORT (INCLUDING NEGLIGENCE OR OTHERWISE) ARISING IN ANY WAY OUT OF THE
USE OF THIS SOFTWARE, EVEN IF ADVISED OF THE POSSIBILITY OF SUCH
DAMAGE.
}
\newpage

\tableofcontents

\newpage

\section{Status}
\input{reqsprios.tex}

\section{What's all about}
This is the \textsl{master} requirment where all other (especially the
initial requirements) depend on. There can only be one master requirment.
\input{reqs/rmtoo.tex}

\section{Initial Requirements}
This is the section containing all the initial requirments.
\input{reqs/Requirements.tex}
\input{reqs/AgileDevelopment.tex}
\input{reqs/Simplicity.tex}
\input{reqs/OpenSource.tex}
\input{reqs/EasyExtensible.tex}
\input{reqs/AutomaticGeneration.tex}
\input{reqs/EasyEditable.tex}
\input{reqs/Documentation.tex}
\input{reqs/EaseOfUse.tex}

\section{Requirements Tags}
Each requirment has a couple of tags and values.  This section
describes all the tags.
\input{reqs/ReqTagName.tex}
\input{reqs/ReqTagType.tex}
\input{reqs/ReqTagInventedBy.tex}
\input{reqs/ReqTagInventedOn.tex}
\input{reqs/ReqTagDescription.tex}
\input{reqs/ReqTagOwner.tex}
\input{reqs/ReqTagStatus.tex}
\input{reqs/Status.tex}
\input{reqs/ReqTagPriority.tex}
\input{reqs/PrioFormat.tex}
\input{reqs/ReqTagClass.tex}
\input{reqs/Class.tex}
\input{reqs/ReqTagEffortEst.tex}
\input{reqs/EftMeasure.tex}
\input{reqs/EftAllowedMeasure.tex}

\section{Input}
\input{reqs/Checks.tex}
\input{reqs/CheckSemantic.tex}
\input{reqs/CheckSyntax.tex}
\input{reqs/CheckGraph.tex}
\input{reqs/CheckGraphOneMaster.tex}
\input{reqs/CheckGraphSCC.tex}
\input{reqs/ReqTagPriorityCheck.tex}

\section{Implementation Decisions}
\input{reqs/UseTxt.tex}
\input{reqs/UsePython.tex}
\input{reqs/Traceability.tex}
\input{reqs/NoDirectedCircles.tex}
\input{reqs/Completed.tex}

\section{Output}
\input{reqs/Output.tex}
\input{reqs/OutputPDF.tex}
\input{reqs/OutputGraph.tex}
\input{reqs/PrioOutputLaTeX.tex}
\input{reqs/PrioOutputInGraph.tex}
\input{reqs/PrioOutputOrderByClass.tex}
\input{reqs/PrioOutputEft.tex}

\section{Emacs Mode}
\input{reqs/EmacsMode.tex}
\input{reqs/EMTraceability.tex}
\input{reqs/EMIndentation.tex}
\input{reqs/EMHighLightTags.tex}
\input{reqs/EMAutoFill.tex}
\input{reqs/EMFlyspellMode.tex}
\input{reqs/EMValueHighlight.tex}

\section{Documentation}
\input{reqs/DocManPage.tex}
\input{reqs/DocSlides.tex}
\input{reqs/ManOverview.tex}
\input{reqs/ManLaTeX.tex}
\input{reqs/ManReqFormat.tex}
\input{reqs/ManArtElabList.tex}
\input{reqs/ManGraph.tex}
\input{reqs/ManEmacsMode.tex}
\input{reqs/ManArtBacklog.tex}

\section{Agile Development Process}
\input{reqs/PrioComputation.tex}
\input{reqs/OutputPrio.tex}

\section{Automatic Creation of Artifacts}
\input{reqs/Makefile.tex}
\input{reqs/MakefileDeps.tex}

\section{Testing}
\input{reqs/Testing.tex}
\input{reqs/TestBeforePack.tex}

\section{Deployment and Packaging}
\input{reqs/Packaging.tex}
\input{reqs/PackDebian.tex}

\end{document}

% \input{reqs/.tex}

